Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-04-17 manuscript/manuscript.tex
minor ms changes

>>>>

Here we define the general background selection process (gBGS) as the polygenic
selection occurring due to the influx of new mutations that have an average
negative selection coefficient over their lifetimes. Such mutations are
destined to either fixation or extinction depending on their selection
coefficient and magnitudes of two sources of evolutionary stochaticity: genetic
drift, scaled by population size, and genetic draft, scaled by other ongoing
selection and the linkage environment. Classic BGS models only consider the
case where linkage is loose (no selective interference) and mutations are
sufficiently deleterious that they cannot fix. Studies have used classic BGS
theory to develop statistical methods to model patterns of genome-wide
diversity (XXX). Here, we extend this line of work in three ways. First,
classic BGS theory assumes all deleterious mutations go extinct, and
consequently cannot accurately model weakly deleterious mutation rates that
drift up and frequency and in some cases fix in the population. We find that
this can bias DFE estimates in cases where weak selection constitutes a large
portion of the DFE. Using the theory of XXX we ameliorate this issue, and find
our method can provide rough genome-wide estimates of the deleterious mutation
rate from the signal of linked polygenic selection. Second, since the theory
predicts diversity levels under weak selection by simultaneously predicting the
rate at which weakly deleterious mutations are substituted, by fitting our
model to human genome-wide data, our model predicts substitution rates across
the genome. We find these predictions substitutions for the features under
selection match observed

According to theory, the extent of linkage in the genome can limit how quickly
polygenic selection can occur in artificially selected organisms. Since the BGS
process is a type of polygenic selection,
